Compiling refinement types to dependent types

### 2020-07-18 tex/paper.tex
Introduce translating typing relations and explain why we need that

\newcommand{\tranctx}{\mu_\Gamma}
\newcommand{\tranty}{\mu_\tau}
\newcommand{\tranterm}{\mu_\varepsilon}

We translate the surface language contexts, types and terms into the corresponding core language entities
using the $\tranctx$, $\tranty$ and $\tranterm$ functions respectively,
which are defined mutually recursively.

>>>>

\newcommand{\tranctx}{\mu_\Gamma}
\newcommand{\tranty}{\mu_\tau}
\newcommand{\tranderiv}{\mu_\vdash}
\newcommand{\tranterm}{\mu_\varepsilon}

We translate the surface language contexts, types and terms into the corresponding core language entities
using the $\tranctx$, $\tranty$ and $\tranderiv$ functions respectively,
which are defined mutually recursively.

Before we dive into defining these functions, $\tranderiv$ deserves a few introductory words.
Although the aim is to translate terms,
what this function really does is translating the surface typing derivation for a given (well-typed) term
into a typing derivation in the core language.
The reason for the extra complexity stems from the \ottdrulename{T-Sub} typing rule.
In particular, this rule invokes the subtyping check, which, in turn, invokes the oracle.
The oracle then might produce a core language term proving that the subtyping relation in question holds,
and the presence of this rule is in some sense a carrier of this proof term.
